Shared Characterizations of Challenging Demands and Job Resources across O*NET Element Classifications

### 2025-09-09 Submission.Rmd
checking for conflicts

>NOTE. grab O\*NET description from desktop (this paragraph only)

@@

The Occupational Information Network (O\*NET) serves as a repository of information broadly descriptive of occupations [@peterson2001understanding]. The O\*NET database consists of hundreds of standardized and occupation-specific descriptors of occupations in the US and these descriptions are frequently updated. We focused on 98 work [activity and context statements](https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3) which O\*NET groups into *activity* categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?). Work *context* statements are grouped into interpersonal relationships (e.g., the context of the job in terms of human interaction processes), physical work conditions (e.g., the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (e.g., the relationships or interactions between the worker and the structural characteristics of the job).

O\*NET collects information about these elements by periodically surveying workers with job characteristic questions, which often have [unique response categories](https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2).  For example, "How responsible is the worker for work outcomes and results of other workers?" has response options ranging from *no responsibility* to *very high responsibility*, while the question, "How often do you use electronic mail in this job?" has options ranging from *never* to *every day*. We retained O\*NET’s response scales while asking for statement relevance, all of which shared the same number of response option categories (5) regardless of semantic label difference. We also retained original O\*NET wording for our item stems, with minor grammatical exceptions^[For example, the worker responsibility question was changed from "How responsible is the worker..." to "How responsible are you..."]. The total number of items on each administered survey was less than 392 (98 characteristics x 4 repeated measurements) because we did not ask for evaluations for 14 O\*NET characteristics that we surmised to have extremely low frequency of affirmative endorsement across respondents (one such excluded characteristic, for example, was "...the extent to which the worker is exposed to radiation on the job").

Participants were first asked to think about whether or not their job could be described as consisting of these job characteristics. If a respondent indicated that any one characteristic was not applicable for their job (e.g., answered *never* or *not at all*), they were not subsequently asked to rate the level of resource (...this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (...this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (...this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment). These ratings were made along a 5--point Likert--type agreement scale with values of (1) Strongly Disagree, (2) Disagree, (3) Neither Agree nor Disagree, (4) Agree, and (5) Strongly Agree. All questions were administered in randomized order within blocks of characteristic, resource, challenge, and hindrance.

@@

Stress was captured via three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019). Responses were provided using a Likert-type scale ranging from (1) Not at All to (5) All the Time. A sample item is, “How often have you had problems relaxing because of your job?”. Coefficient alpha [@cronbach1951coefficient] was 0.85 in this sample.

@@

Four items from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019) were used to assess burnout. Again, responses were provided using a Likert-type scale ranging from (1) Not at All to (5) All the Time. A sample item is, “How often have you felt worn out?”. Within our sample, coefficient alpha was 0.85.

@@

Respondents were asked to think about their primary job, and each administered survey branched content dependent on whether or not the respondent's job could be described as consisting of the different O\*NET job characteristics. Participants were compensated six USD for their participation (the estimated time commitment pre-administration was 45 minutes). See Figure \@ref(fig:onetviz) for a visual representation of the survey experience.

@@

>NOTE. Get rid of Fig 3 - present the histograms as indicating that "not everyone agrees that a characterisitic is a... (challenge, hindrance, resource)", then highlight items with greatest discrepancy to provide flavor to the histograms (flip the current $\P$ ordering)

H1 posits that *not everyone agrees* that a characterisitic is a hindrance, challenge, or resource. Figure \@ref(fig:overallhist) presents standard deviations of characteristic rating across all rated items. Here,the *spread* of difference exhibits wider distributions of (dis)agreement for challenge and resource ratings (and a relatively more leptokurtic distribution of (dis)agreement for hindrances). The distributions demonstrate that some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement. This points to *hindrances*, in particular, as being likely amenable to future probing regarding moderating conditions. A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference ($\chi^2_{`r lookie$df`}$ = `r lookie$statistic[[1]]`, *p* < .01).

Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) present the most extreme examples of characteristic variability in the form of the 8-most *consistently rated* and *inconsistently rated* resources, challenges, and demands.[^onlinelist] Figure \@ref(fig:combinegraphs) presents the *most consistently agreed on* resources, hindrances, and challenges as indexed by lowest empirical standard deviations, while Figure \@ref(fig:combinegraphs2) presents the characteristics with the greatest amount of *disagreement* across workers. The figures again highlight that what is perceived as resource and challenge tends to be relatively agreed upon (the range of the "lowest 8" resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`). However, there is considerably less agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the *greatest agreement* still ranging in fairly large standard deviations (ranging from `r min(tophindrance$sd)` to `r max(tophindrance$sd)`). In sum, these results provide some collective support for H1, and  particularly so for hindrances, which are differently experienced across our raters.

@@

The second hypothesis, similarly oriented to H1, stated that job characteristics would not be *uniquely* categorized as a resource or demand. We explore this via pattern of correlation similar in intent to @campbell1959convergent's multi--trait multi--method matrix. Table 1 provides the correlations among the O\*NET "scale"--level groupings^[Survey items are grouped by O\*NET into categories of Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc). These groupings were not presented to respondents but are leveraged here to facilitate interpretation of characteristic association.] across evaluations as resource, challenge, and hindrance. Here would expect trivial correlations if job characteristics *were* uniquely categorized. First, the average correlation within all resource categories (variables 1 through 7 in Table 1) was .43 (*SD* = .13, coefficient magnitude ranges from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, *M* = .43, *SD* =.16). Hindrance categories, however, had less differentiation across categories, with relatively elevated correlations ranging from .33 to .86, *M* = .62, *SD* = .17. When people perceive hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater differentiation.

>>>>

@@

The Occupational Information Network (O\*NET) serves as a repository of information broadly descriptive of occupations [@peterson2001understanding] and these descriptions are frequently updated. We focused on 98 work [activity and context statements](https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3) which O\*NET groups into *activity* categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?). Work *context* statements are grouped into interpersonal relationships (e.g., the context of the job in terms of human interaction processes), physical work conditions (e.g., the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (e.g., the relationships or interactions between the worker and the structural characteristics of the job).

O\*NET collects information about these elements by periodically surveying workers with job characteristic questions, each of which often has [unique response categories](https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2).  For example, "How responsible is the worker for work outcomes and results of other workers?" has response options ranging from *no responsibility* to *very high responsibility*, while the question, "How often do you use electronic mail in this job?" has options ranging from *never* to *every day*. For the current investigation, O\*NET’s response scales were retained when asking for *statement relevance* (all response scales shared the same *number* of response option categories [5] regardless of semantic labeling). We also retained the original O\*NET wording for our item stems, with minor grammatical referent exceptions^[For example, the worker responsibility question was changed from "How responsible is the worker..." to "How responsible are you..."]. The total number of items on each administered survey was less than 392 (98 characteristics x 4 repeated measurements) because we did not ask for evaluations for 14 O\*NET characteristics that we surmised to have extremely low frequency of affirmative endorsement across respondents (one such excluded characteristic, for example, was "...the extent to which the worker is exposed to radiation on the job").

Participants were first asked to consider whether or not their job could reasonably be described as consisting of each job characteristic. If a respondent indicated that any one characteristic was not applicable for their job (e.g., answered *never* or *not at all*), they were not subsequently asked to rate the level of resource (...this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (...this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (...this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment). The challenge, hindrance, and resource ratings were made along a 5--point Likert--type agreement scale with values of (1) Strongly Disagree, (2) Disagree, (3) Neither Agree nor Disagree, (4) Agree, and (5) Strongly Agree. All questions were administered in randomized order within blocks of characteristic, resource, challenge, and hindrance.

@@

Stress was captured via three items taken from the Copenhagen Psychosocial Questionnaire [@burr2019third]. Responses were provided using a Likert-type scale ranging from (1) Not at All to (5) All the Time. A sample item is, “How often have you had problems relaxing because of your job?”. Coefficient alpha [@cronbach1951coefficient] was 0.85 in this sample.

@@

Four items from the Copenhagen Psychosocial Questionnaire [@burr2019third] were used to assess burnout. Again, responses were provided using a Likert-type scale ranging from (1) Not at All to (5) All the Time. A sample item is, “How often have you felt worn out?”. Within our sample, coefficient alpha was 0.85.

@@

Respondents were asked to think only about their *primary* job, and each administered survey branched content dependent on whether or not this job could be described as consisting of the different O\*NET job characteristics. Participants were compensated six USD for their participation (the estimated time commitment pre-administration was 45 minutes). See Figure \@ref(fig:onetviz) for a visual representation of the survey experience.

@@

H1 posits that *not everyone agrees* that a characterisitic is a hindrance, challenge, or resource. Figure \@ref(fig:overallhist) presents standard deviations of characteristic rating across all rated items. Here,the *spread* of difference exhibits wider distributions of disagreement for challenge and resource ratings (and a relatively more leptokurtic distribution of disagreement for hindrances). The distributions demonstrate that some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement. A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference ($\chi^2_{`r lookie$df`}$ = `r lookie$statistic[[1]]`, *p* < .01). This points to *hindrances*, in particular, as being most generally amenable to future probing regarding moderating conditions.

To provide context to the Figure \@ref(fig:overallhist) distributions, we present the Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) present the most extreme examples of characteristic variability in the form of the 8-most *similarly rated* (Figure \@ref(fig:combinegraphs)) and *dissimilarly rated* resources, challenges, and demands (Figure \@ref(fig:combinegraphs2)).[^onlinelist] These figures again highlight that what is perceived as resource and challenge tends to be relatively agreed upon (the range of the "lowest 8" resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`). However, there is considerably less agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the *greatest agreement* still ranging in fairly large standard deviations (ranging from `r min(tophindrance$sd)` to `r max(tophindrance$sd)`). In sum, these results provide support for H1, and  particularly so for hindrances, which are differently experienced across our raters.

@@

The second hypothesis, similarly oriented to H1, stated that job characteristics would not be *uniquely* categorized as a resource or demand. We explore this via pattern of correlation similar in intent to @campbell1959convergent's multi--trait multi--method matrix. Table 1 provides the correlations among the O\*NET "scale"--level groupings^[Survey items are grouped by O\*NET into categories of Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc). These groupings were not presented to respondents but are leveraged here to facilitate interpretation of characteristic association.] across evaluations as resource, challenge, and hindrance. Here one would expect only trivial associations if job characteristics *were* uniquely categorized. First, the average correlation within all resource categories (variables 1 through 7 in Table 1) was .43 (*SD* = .13, coefficient magnitude ranges from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, *M* = .43, *SD* =.16). Job hindrances, however, exhibited less differentiation across categories, with relatively elevated correlations ranging from .33 to .86, *M* = .62, *SD* = .17. When people perceive hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater selectivity.

>STOPPED HERE: Too much description
